% \begin{abstract}
Blockchain protocols such as bitcoin provide decentralized consensus
mechanisms based on proofs of work (PoWs).
%
In this work we introduce and instantiate a new primitive for blockchain protocols called Noninteractive-Proofs-of-Proof-of-Work (NIPoPoWs) which can be adapted into existing cryptocurrencies to support more efficient clients.
Unlike a traditional blockchain client which must verify the entire
linearly-growing chain of PoWs, clients based on NIPoPoWs require resources
only logarithmic in the length of the blockchain.

%This proof is linear in size in
%the case of both a full node or an SPV. Using lite proofs-of-proof-of-work,
%these proofs can become sublinear, but require interactivity. We modify PoPoWs
%to produce non-interactive proofs. We describe how exactly these proofs can be
%constructed. 
NIPoPoWs solve two important open questions for PoW based consensus
protocols. Specifically the problem  
of constructing efficient transaction verification clients, sometimes called
``simple payment verification'' or SPV, and the problem of constructing
efficient sidechain proofs. 
%
%Sidechains is a mechanism that enables 
% experimenting with different consensus rules while avoid hard forks. 
%Secure implementation to transfer a coin between sidechains, a transaction must include a
%proof that proof-of-work has been performed. t
%
We provide a formal model for NIPoPoWs. We prove our proofs are secure in our
model via a cryptographic reduction argument and succint in size. We provide
simulations and experimental data to measure concrete communication efficiency
and security. 
Finally, we provide two ways that our NIPoPoWs can be adopted by
existing blockchain protocols, first via a soft fork, that enables the 
adoption of the NIPoPoW related data structures
as part of the underlying consensus mechanism, 
and second via a new update mechanism 
that we term a ``velvet fork'' and enables to harness some of
the performance benefits of NIPoPoWs even without reaching consensus about its use
across nodes. The velvet fork scheme is of independent interest to enable
consensus layer upgrades without requiring an agreement by miner majority.

%This construction provides a solution to the
%previously open problem of building secure and efficient sidechains. Our
%construction is of general interest and can be applied to any PoW-based
%cryptocurrency.
% \end{abstract}

