\section{Formal security treatment}
\label{sec:security-full}

Here, we give a formal treatment of the security proof which was sketched in
Section~\ref{sec:security}.

Assume $t$ adversarial and $n$ total parties, each with $q$
PoW random oracle queries per round. We will call a query to the
RO $\mu$-\textit{successful} if the RO returns a value $h$
such that $h \leq 2^{-\mu}T$.

We define boolean random variables $X_r^\mu$, $Y_r^\mu$ and $Z_r^\mu$. Fix some
round $r$, query index $j$ and adversarial party index $k$ (out of $t$). If at
round $i$ an honest party obtains a PoW with $id < 2^{-\mu}T$, set $X_r^\mu =
1$, otherwise $X_r^\mu = 0$. If at round $r$ exactly one honest party obtains a
PoW with $id < 2^{-\mu}T$, set $Y_r^\mu = 1$, otherwise $Y_r^\mu = 0$. If at
round $r$ the $j$-th query of the $k$-th corrupted party is $\mu$-successful,
set $Z^\mu_{ijk} = 1$, otherwise $Z^\mu_{ijk} = 0$. Let $Z^\mu_r = \sum_{k=1}^t
\sum_{j=1}^q Z^\mu_{ijk}$. For a set of rounds $S$, let $X^\mu(S) = \sum_{r \in
S} X_r$ and similarly define $Y^\mu(S), Z^\mu(S)$.

\begin{definition}[Typical execution]
    An execution of the protocol is $(\epsilon, \eta)$-\textit{typical} if:

    \textnormal{\bf Block counts don't deviate.}
    For all $\mu \geq 0$ and any set $S$ of consecutive rounds
    with $|S| \geq 2^\mu \eta\kappa$, we have:

    \begin{itemize}
        \item $(1 - \epsilon)E[X^\mu(S)] < X^\mu(S) < (1 + \epsilon)E[X^\mu(S)]$ and $(1 - \epsilon)E[Y^\mu(S)] < Y^\mu(s)$.
        \item $Z^\mu(S) < (1 + \epsilon)E[Z^\mu(S)]$.
    \end{itemize}

    \textnormal{\bf Round count doesn't deviate.}
    Let $S$ be a set of consecutive rounds such that $Z^\mu(S)
    \geq k$ for some security parameter $k$. Then $|S| \geq (1 -
    \epsilon)2^\mu\frac{k}{pqt}$ with overwhelming probability in $k$.

    \textnormal{\bf Chain regularity.}
    No insertions, no copies, and no predictions \cite{backbone} have occurred.
\end{definition}

\begin{theorem}[Typicality]
\label{thm.typicality}
Executions are $(\epsilon, \eta)$-typical with overwhelming
probability in $\kappa$.
\end{theorem}
\import{./}{proofs/typicality.tex}

The following lemma is at the heart of the security proof that will follow.

\begin{lemma}\label{lem.level-comparison}
    Suppose $S$ is a set of consecutive rounds $r_1 \ldots r_2$
    and $\chain_B$ is
    a chain adopted by an honest party at round $r_2$ of a typical execution.
    Let $\chain_B^S = \{b \in
    \chain_B: b \textnormal{ was generated during } S\}$. Let $\mu_\mathcal{A},
    \mu_B \in \mathbb{N}$. Suppose $\chain_B^S\upchain^{\mu_B}$ is good.
    Suppose $\chain'_\mathcal{A}$ is a $\mu_\mathcal{A}$-superchain containing
    only adversarially generated blocks generated during $S$ and suppose that
    $|\chain'_\mathcal{A}| \geq k$.
    Then
    $2^{\mu_\mathcal{A}}|\chain'_\mathcal{A}| < \frac{1}{3}2^{\mu_B}|\chain_B^S\upchain^{\mu_B}|$.
\end{lemma}
\import{./}{proofs/levelcomparison.tex}

\begin{definition}[Adequate level of honest proof]
Let $\pi$ be an honestly generated proof constructed upon some adopted chain
$\chain$ and let $b \in \pi$.

Then $\mu'$ is defined as  $\mu' = \max\{\mu: |\pi\{b:\}\upchain^\mu| \geq
\max(m + 1, (1 - \delta)2^{-\mu}|\pi\{b:\}\upchain^\mu\downchain|)\}$.
We call $\mu'$ the \textit{adequate} level of proof $\pi$ with respect to
block $b$ with security parameters $\delta$ and $m$. Note that the adequate
level of a proof is a function of both the proof $\pi$ and the chosen block $b$.
\end{definition}

\begin{restatable}{lemma}{restateThmAllBlocks}\label{lem.allblocks}
Let $\pi$ be some honest proof generated with security parameters $\delta, m$.
Let $\chain$ be the underlying chain, $b \in \chain$ be any block and $\mu'$ be
the adequate level of the proof with respect to $b$ and the same security
parameters.

Then $\chain\{b:\}\upchain^{\mu'} = \pi\{b:\}\upchain^{\mu'}$.
\end{restatable}
\import{./}{proofs/allblocks.tex}

\begin{lemma}
Suppose the verifier evaluates $\pi_\mathcal{A} \geq \pi_B$ in a protocol
interaction where $B$ is honest and assume during the comparison that the
compared level of the honest party is $\mu_B$. Let $b =
\textsf{LCA}(\pi_\mathcal{A}, \pi_B)$ and let $\mu_B'$ be the adequate
level of $\pi_B$ with respect to $b$. Then $\mu_B' \geq \mu_B$.
\end{lemma}
\import{./}{proofs/leveladequacy.tex}

\restateThmSecurity*
\import{./}{proofs/security.tex}

\begin{remark}[Variance attacks]
\label{rmk.variance}
The critical issue addressed by this security proof is to avoid Bahack-style
attack \cite{bahack} where the adversary constructs ``lucky'' high-difficulty
superblocks without filling in the underlying proof-of-work in the lower
levels. Observe that, while setting $m = 1$ ``preserves'' the proof-of-work in
the sense that expectations remain the same, the probability of an adversarial
attack becomes approximately proportional to the adversary power if the
adversary follows a suitable strategy (for a description of such a strategy,
see the parameterization section). With higher values of $m$, the probability of
an adversarial attack drops exponentially in $m$, even though they maintain constant
computational power, and hence satisfy a strong notion of security.
\end{remark}

\noindent\textbf{Remark.}
Intuitively, the attack of Section~\ref{sec:attack} is neutralized, because
our prover takes ``goodness'' of blockchains into account and the verifier
does not compare proofs strictly at the same level.

\noindent\textbf{Remark.}
We have explored security in the \emph{synchronous} model. We remark that the
same construction can work in a \emph{partially synchronous} model by setting
$k' = 2k$, where $k'$ is the security parameter of the partially synchronous
model and $k$ is the security parameter in the synchronous model. We leave the
full treatment of this for future work.

\subsection{Infix security}
We observe that now that we have proven the modified suffix construction secure,
the security of infix proofs follows without any modifications in the infix
construction. We formally state this in the following corollary.

\begin{restatable}{corollary}{restateCrlyInfixSecurity}
\label{crly.infix-security}
Under honest majority, the infix NIPoPoW protocol $(P, V)$ is secure for all
computable infix-sensitive $k$-stable monotonic predicates $Q$, except with
negligible probability in $\kappa$.
\end{restatable}
\import{./}{proofs/infixsecurity.tex}
