\section{Security}

Based on the attack explored above, it is now easy to see that our construction
can be patched in a straightforward manner to achieve security. In particular,
since the manner in which the adversary was able to subvert the prover was by
the violation of \emph{goodness}, we can mandate that the prover only tries to
use succinct proofs to prove claims about chains that are
\emph{good at every level}. In case goodness is violated, the prover simply
falls back to providing the whole chain. This allows us to argue that the
construction is secure by distinguishing two cases. In case goodness is
violated, the honest prover will fall back to providing the whole chain, in
which case security will be reduced to the security of the standard
blockchain protocol choosing the longest $0$-chain. In case goodness is not
violated, we will argue that the adversary is unable to win in these
comparisons.

The previous construction was designed to prevent Bahack-style
attacks~\cite{bahack}, where the adversary constructs ``lucky'' high-difficulty
superblocks without filling in the underlying proof-of-work in the lower levels.
We now patch our protocol which, while retaining this highlevel approach, adds a
defence against the double-spending attack of Section~\ref{sec:attack}. The
attack is neutralized since our verifier is more permissive, allowing the prover
to construct a proof that takes superquality ``goodness'' into account when
comparing forks. The modified construction is shown in
Algorithm~\ref{alg.nipopow-prover-patched}. The algorithm has been modified to
check the current portion of the subchain $\alpha$ for \emph{goodness} prior to
moving to the lower superchain level. If goodness is indeed maintained at the
current level $\mu$, the prover only tries to cover the span of the last $m$
blocks of level $\mu$ at level $\mu - 1$, as seen in
Line~\ref{alg.nipopow-prover-patched.good}. Otherwise, if goodness is violated
at the part of the subchain $\alpha$ at level $\mu$, then the prover completely
ignores level $\mu$ and tries to use the lower level $\mu - 1$ to cover the
whole span of $\alpha$.

Only the concrete prover needs to be modified. The verifier and $\leq_m$
operator remain as defined previously.

\import{./}{algorithms/alg.nipopow-prover-patched.tex}

To aid intuition, we will first give a sketch of the proof before giving the
full technical proof.

\begin{restatable}[Security]{theorem}{restateThmSecurity}
    \label{thm.security}
    Assuming honest majority, the non-interactive proofs-of-proof-of-work
    construction for computable $k$-stable monotonic suffix-sensitive predicates
    is secure with overwhelming probability in $\kappa$.
\end{restatable}
\begin{proof}[Sketch]
Suppose an adversary produces a proof $\pi_\mathcal{A}$ and an honest
party produces a proof $\pi_B$ such that the two proofs cause the predicate $Q$
to evaluate to different values, while at the same time all honest parties have
agreed that the correct value is the one obtained by $\pi_B$. Because of
bitcoin's security, $\mathcal{A}$ will be unable to make these claims for an
actual underlying 0-level chain.

We now argue that the operator $\leq_m$ will
signal in favour of the honest parties.
Suppose $b$ is the LCA block between $\pi_\mathcal{A}$ and $\pi_B$. If the chain
forks at $b$, there can be no more adversarial blocks after $b$ than honest
blocks after $b$, provided there are at least $k$ honest blocks (due to the
Common Prefix property). We will now argue that, further, there can be no more
disjoint $\mu_\mathcal{A}$-level superblocks than honest $\mu_B$-level
superblocks after $b$.

To see this, let $b$ be an honest block generated at some round $r_1$ and let
the honest proof have been generated at some round $r_3$. Then take the sequence
of consecutive rounds $S = (r_1, \cdots, r_3)$. Because the verifier requires at
least $m$ blocks from each of the provers, the adversary must have $m$
$\mu_\mathcal{A}$-superblocks in $\pi_\mathcal{A}\{b:\}$ which are not in
$\pi_B\{b:\}$. Therefore, using a negative binomial tail bound argument, we see
that $|S|$ must be long; intuitively, it takes a long time to produce a lot of
blocks $|\pi_\mathcal{A}\{b:\}|$. Given that $|S|$ is long and that the honest
parties have more mining power, they must have been able to produce a longer
$\pi_B\{b:\}$ argument (of course, this comparison will have the superchain
lengths weighted by $2^{\mu_\mathcal{A}}, 2^{\mu_B}$ respectively). To prove
this, we use a binomial tail bound argument; intuitively, given a long time
$|S|$, a lot of $\mu_B$-superblocks $|\pi_B\{b:\}|$ will have been honestly
produced.

We therefore have a fixed value for the length of the adversarial argument, a
negative binomial random variable for the number of rounds, and a binomial
random variable for the length of the honest argument. By taking the
expectations of the above random variables and applying a Chernoff bound, we see
that the actual values will be close to their means with overwhelming
probability, completing the proof.
\Qed
\end{proof}

\noindent\textbf{Remark.}
Observe that, while setting $m = 1$ ``preserves'' the proof-of-work in the sense
that expectations remain the same, the probability of an adversarial attack
becomes approximately proportional to the adversary power if the adversary
follows a suitable strategy (for a description of such a strategy, see the
parameterization section). With higher values of $m$, the probability of an
adversarial attack drops exponentially in $m$, even though they maintain
constant computational power, and hence satisfy a strong notion of security.

We now go on to formalize the above proof sketch.

Assume $t$ adversarial and $n$ total parties, each with $q$
PoW random oracle queries per round. We will call a query to the
RO $\mu$-\textit{successful} if the RO returns a value $h$
such that $h \leq 2^{-\mu}T$.

We define boolean random variables $X_r^\mu$, $Y_r^\mu$ and $Z_r^\mu$. Fix some
round $r$, query index $j$ and adversarial party index $k$ (out of $t$). If at
round $i$ an honest party obtains a PoW with $id < 2^{-\mu}T$, set $X_r^\mu =
1$, otherwise $X_r^\mu = 0$. If at round $r$ exactly one honest party obtains a
PoW with $id < 2^{-\mu}T$, set $Y_r^\mu = 1$, otherwise $Y_r^\mu = 0$. If at
round $r$ the $j$-th query of the $k$-th corrupted party is $\mu$-successful,
set $Z^\mu_{ijk} = 1$, otherwise $Z^\mu_{ijk} = 0$. Let $Z^\mu_r = \sum_{k=1}^t
\sum_{j=1}^q Z^\mu_{ijk}$. For a set of rounds $S$, let $X^\mu(S) = \sum_{r \in
S} X_r$ and similarly define $Y^\mu(S), Z^\mu(S)$.

\begin{definition}[Typical execution]
    An execution of the protocol is $(\epsilon, \eta)$-\textit{typical} if:

    \textnormal{\bf Block counts don't deviate.}
    For all $\mu \geq 0$ and any set $S$ of consecutive rounds
    with $|S| \geq 2^\mu \eta\kappa$, we have:

    \begin{itemize}
        \item $(1 - \epsilon)E[X^\mu(S)] < X^\mu(S) < (1 + \epsilon)E[X^\mu(S)]$ and $(1 - \epsilon)E[Y^\mu(S)] < Y^\mu(s)$.
        \item $Z^\mu(S) < (1 + \epsilon)E[Z^\mu(S)]$.
    \end{itemize}

    \textnormal{\bf Round count doesn't deviate.}
    Let $S$ be a set of consecutive rounds such that $Z^\mu(S)
    \geq k$ for some security parameter $k$. Then $|S| \geq (1 -
    \epsilon)2^\mu\frac{k}{pqt}$ with overwhelming probability in $k$.

    \textnormal{\bf Chain regularity.}
    No insertions, no copies, and no predictions \cite{backbone} have occurred.
\end{definition}

\begin{theorem}[Typicality]
\label{thm.typicality}
Executions are $(\epsilon, \eta)$-typical with overwhelming
probability in $\kappa$.
\end{theorem}
\import{./}{proofs/typicality.tex}

The following lemma is at the heart of the security proof that will follow.

\begin{lemma}\label{lem.level-comparison}
    Suppose $S$ is a set of consecutive rounds $r_1 \ldots r_2$
    and $\chain_B$ is
    a chain adopted by an honest party at round $r_2$ of a typical execution.
    Let $\chain_B^S = \{b \in
    \chain_B: b \textnormal{ was generated during } S\}$. Let $\mu_\mathcal{A},
    \mu_B \in \mathbb{N}$. Suppose $\chain_B^S\upchain^{\mu_B}$ is good.
    Suppose $\chain'_\mathcal{A}$ is a $\mu_\mathcal{A}$-superchain containing
    only adversarially generated blocks generated during $S$ and suppose that
    $|\chain'_\mathcal{A}| \geq k$.
    Then
    $2^{\mu_\mathcal{A}}|\chain'_\mathcal{A}| < \frac{1}{3}2^{\mu_B}|\chain_B^S\upchain^{\mu_B}|$.
\end{lemma}
\import{./}{proofs/levelcomparison.tex}

\begin{definition}[Adequate level of honest proof]
Let $\pi$ be an honestly generated proof constructed upon some adopted chain
$\chain$ and let $b \in \pi$.

Then $\mu'$ is defined as  $\mu' = \max\{\mu: |\pi\{b:\}\upchain^\mu| \geq
\max(m + 1, (1 - \delta)2^{-\mu}|\pi\{b:\}\upchain^\mu\downchain|)\}$.
We call $\mu'$ the \textit{adequate} level of proof $\pi$ with respect to
block $b$ with security parameters $\delta$ and $m$. Note that the adequate
level of a proof is a function of both the proof $\pi$ and the chosen block $b$.
\end{definition}

\begin{restatable}{lemma}{restateThmAllBlocks}\label{lem.allblocks}
Let $\pi$ be some honest proof generated with security parameters $\delta, m$.
Let $\chain$ be the underlying chain, $b \in \chain$ be any block and $\mu'$ be
the adequate level of the proof with respect to $b$ and the same security
parameters.

Then $\chain\{b:\}\upchain^{\mu'} = \pi\{b:\}\upchain^{\mu'}$.
\end{restatable}
\import{./}{proofs/allblocks.tex}

\begin{lemma}
Suppose the verifier evaluates $\pi_\mathcal{A} \geq \pi_B$ in a protocol
interaction where $B$ is honest and assume during the comparison that the
compared level of the honest party is $\mu_B$. Let $b =
\textsf{LCA}(\pi_\mathcal{A}, \pi_B)$ and let $\mu_B'$ be the adequate
level of $\pi_B$ with respect to $b$. Then $\mu_B' \geq \mu_B$.
\end{lemma}
\import{./}{proofs/leveladequacy.tex}

\restateThmSecurity*
\import{./}{proofs/security.tex}

\begin{remark}[Variance attacks]
\label{rmk.variance}
The critical issue addressed by this security proof is to avoid Bahack-style
attack \cite{bahack} where the adversary constructs ``lucky'' high-difficulty
superblocks without filling in the underlying proof-of-work in the lower
levels. Observe that, while setting $m = 1$ ``preserves'' the proof-of-work in
the sense that expectations remain the same, the probability of an adversarial
attack becomes approximately proportional to the adversary power if the
adversary follows a suitable strategy (for a description of such a strategy,
see the parameterization section). With higher values of $m$, the probability of
an adversarial attack drops exponentially in $m$, even though they maintain constant
computational power, and hence satisfy a strong notion of security.
\end{remark}

\noindent\textbf{Remark.}
Intuitively, the attack of Section~\ref{sec:attack} is neutralized, because
our prover takes ``goodness'' of blockchains into account and the verifier
does not compare proofs strictly at the same level.

\noindent\textbf{Remark.}
We have explored security in the \emph{synchronous} model. We remark that the
same construction can work in a \emph{partially synchronous} model by setting
$k' = 2k$, where $k'$ is the security parameter of the partially synchronous
model and $k$ is the security parameter in the synchronous model. We leave the
full treatment of this for future work.

\subsection{Infix security}
We observe that now that we have proven the modified suffix construction secure,
the security of infix proofs follows without any modifications in the infix
construction. We formally state this in the following corollary.

\begin{restatable}{corollary}{restateCrlyInfixSecurity}
\label{crly.infix-security}
Under honest majority, the infix NIPoPoW protocol $(P, V)$ is secure for all
computable infix-sensitive $k$-stable monotonic predicates $Q$, except with
negligible probability in $\kappa$.
\end{restatable}
\import{./}{proofs/infixsecurity.tex}
